FIXME

### 2013-08-28 writeups/proposal/proposal.tex
foo
Former-commit-id: db40a64f155c5fdbdd37ef6cd30b13ceabba8714 [formerly 2c22df825f77559db5b662b556f138f3320d27c6]
Former-commit-id: cadab7c2f658b38996009f77c804caf809036110

TODO: Introduce PMI \cite{Farahat2004}

TODO: Comparison to ACT-R: Virtually equivalent for large corpora \cite{Farahat2004}

@@

\cite{Douglass2010}

TODO: SNIF-ACT \cite{Fu2007} \cite{Pirolli2003}

>>>>

\textcite{Farahat2004} introduced the Pointwise Mutual Information (PMI) index that also measures strength of association between two terms.
It is based on the co-occurrence count between pair-wise observations of terms, similar to ACT-R's strength of association.
The PMI index is included in Equation \eqref{eqPMI}.

\begin{equation}
  \label{eqPMI}
  PMI(y,x) = log \frac{p(y|x)}{p(y)}
\end{equation}

This PMI equation is identical to ACT-R's strength of association ($S_{ji}$) equation for large datasets.
Once the number of occurrences is large enough such that the probability of observing any particular contextual element ($p(x)$) is near zero, then ACT-R's strength of association index simplifies to the PMI equation.

@@

ACT-R's strength of association ($S_{ji}$) and the equivalent pointwise mutual information index ($PMI_{ji}$) have been shown to scale well for large corpora.
\textcite{Douglass2010} implemented the large-scale version of $S_{ji}$ in Erlang.
The wall-clock time required for a declarative memory retrieval request scaled linearly with the size of declarative memory with this implementation.
Retrieval times were around one second with the largest declarative memory that contained over one million associations (co-occurrence pairs).

The SNIF-ACT framework is also based on the large-scale version of $S_{ji}$, and scales well when working with a large-scale search query database for internet search \parencites{Fu2007,Pirolli2003}.
The $S_{ji}$ values were based on a 118GB local database of 10 million pages of the Stanford Webbase Project.
So this implementation did not fit into RAM, but a spinning-disk database implementation still scaled well enough for reasonably fast retrieval times for $S_{ji}$ values.

The SNIF-ACT model uses the strength of association to measure the relationship between the words in a search query and the words contained in each query result.
A higher $S_{ji}$ between a query and a result means that the result is a better fit for the query, and that the user is more likely to click on that link.
The links that user chose in experimental testing were largely predictive of the strength of association measure.
The predictive power of the SNIF-ACT model went above and beyond what would be predicted by simply assuming that the user always clicks on the first link in the search results page.
